White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2018-01-22 papers/wdmerger_II/paper.tex
Clarify a footnote

We terminate the simulation at $t = 9$ seconds, as we have found that for this
particular setup, all of the significant burning has completed by this time\footnote{In
some simulations at high resolution we were mainly interested in seeing when the
detonation happened, and we terminated the simulation at that point to save
computational cycles. We show nucleosynthesis results only for those simulations
that had completed the nuclear burning.}. At
this point, the total energy on the domain has become positive, typically about
$10^{51}$ ergs, and has stopped increasing. This means that the system has become
unbound due to nuclear energy release, and that no further meaningful nuclear energy
generation is occurring. In our discussions below, it helps to have some other
anchoring points in time when significant events occur. We arbitrarily define the
collision time, $t_{\rm c}$, as the time when the density at the center of the grid
first reaches $10^2\ \text{g / cm}^3$. This is reached only when the WDs meet at the
center of the domain. We define the detonation time, $t_{\rm d}$, as the time when the
temperature first reaches $4.5 \times 10^9\ \text{K}$. This is also an arbitrary
threshold, but we have found empirically that this temperature is only reached in
the collision when a detonation is formed.

>>>>

We terminate the simulation at $t = 9$ seconds, as we have found that for this
particular setup, all of the significant burning has completed by this time\footnote{In
some simulations we were mainly interested in seeing when the detonation happened, and
we terminated the simulation at that point. We show nucleosynthesis results only for
those simulations that had completed nuclear burning.}. At
this point, the total energy on the domain has become positive, typically about
$10^{51}$ ergs, and has stopped increasing. This means that the system has become
unbound due to nuclear energy release, and that no further meaningful nuclear energy
generation is occurring. In our discussions below, it helps to have some other
anchoring points in time when significant events occur. We arbitrarily define the
collision time, $t_{\rm c}$, as the time when the density at the center of the grid
first reaches $10^2\ \text{g / cm}^3$. This is reached only when the WDs meet at the
center of the domain. We define the detonation time, $t_{\rm d}$, as the time when the
temperature first reaches $4.5 \times 10^9\ \text{K}$. This is also an arbitrary
threshold, but we have found empirically that this temperature is only reached in
the collision when a detonation is formed.
